Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
describe the objectives of the experimental evaluation

This section is split into three parts. Section~\ref{experimental-objectives} describes the experimental objectives, while Section~\ref{experimental-setup} discusses the experimental setup and the employed benchmarks. Section~\ref{experimental-results} describes the experimental results related to the application of CEGIS to standard control system benchmarks extracted from the literature.

@@

>>>>

This section is split into three parts. Section~\ref{experimental-setup} discusses 
the experimental setup and the employed benchmarks, while Section~\ref{experimental-objectives} 
describes the experimental objectives. Section~\ref{experimental-results} describes the experimental 
results related to the application of CEGIS to the standard closed-loop control system benchmarks 
described in Section~\ref{experimental-setup}.

@@

Using the closed-loop control system benchmarks described in Section~\ref{experimental-setup}, 
the experimental evaluation of the present approach aims to answer two research questions:
%
\begin{enumerate}
	\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to FWL controller synthesis 
	obtain upon synthesizing/verifying benchmarks that compose the specified suite?
  \item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible solution in reasonable time
	considering robust stability of FWL digital controllers?	
\end{enumerate}
